Segmentation of Electron Microscopy Images for Connectomics

### 2018-05-01 papers/quals2018/3_evaluation.tex
quals: added method and evaluation from eccv submission
quals: major updates to structure

@@

Our proposed method is designed for very large connectomics datasets. 
Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
The following datasets contain 4 times more volume than the CREMI datasets. 
\\~\\
%\subsubsection{Kasthuri}
\noindent\textbf{Kasthuri}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
This dataset is $5342 \times 3618 \times 338$ voxels in size. 
The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
We evaluate our methods using the left cylinder of this 3-cylinder dataset. 
We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. 
We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.
\\~\\
%\subsubsection{FlyEM}
\noindent\textbf{FlyEM}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The mushroom body in this species is the primary site of associative learning. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $999 \times 999 \times 999$ voxels.

%\subsubsection{Fib-25}
%\noindent\textbf{Fib-25}
%The Fib-25 dataset comes from the visual system of a \textit{Drosophila} fly~\cite{takemura2015synaptic}. This sample is %imaged at a resolution of $\SI[product-units=single]{8 x 8 x 8}{\nano\meter}^3$ and has $2588 \times 2108 \times 2876$ %voxels representing a volume of $\SI[product-units=single]{23.0 x 16.9 x 23.0}{\micro\meter}^3$. 
%There is currently a reconstruction challenge based on this sample.

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
%\label{sec:neuroproof}
%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et al.~\cite{funke2017deep} demonstrates superior performance of such methods over existing ones on anisotropic data. 
We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
\\~\\
\noindent\textbf{Graph Generation}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
% Although the voxels vary between different datasets, the physical space remains constant. 
\\~\\
\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
The supplemental material includes information on the experiments that determined these final parameters. 
We provide all parameters of the final network in the supplemental material. 
There are $11,456,241$ learnable parameters in our final architecture. 
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after 330 epochs.

%\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and ten negative examples. 
With probability 0.5, an example is reflected across the $xy$-plane. 
We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.
\\~\\
\noindent\textbf{Graph Partition}
%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
%Higher values of $\beta$ encourage over-segmentation.
Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.99]$. 
For our multicut analysis we use $\beta = 0.95$ (Sec.~\ref{sec:optimization}).

>>>>

\begin{figure}[t]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
	\end{minipage}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}. These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
	\label{fig:skeletonization}
\end{figure}

\begin{figure}[t]
	\begin{minipage}{0.4\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.55\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Geometric constraints for region merging. We show two region merging proposals. On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape. Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
	\label{fig:turn-radii}
\end{figure}

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

Our proposed method is designed for very large connectomics datasets. 
Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
The following datasets contain 4 times more volume than the CREMI datasets. 
The first, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
This dataset is $5342 \times 3618 \times 338$ voxels in size. 
The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
We train one of these halves and test on the other.
Our second dataset, called FlyEM, comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et al.~\cite{funke2017deep} demonstrates superior performance of such methods over existing ones on anisotropic data. 
We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
\\~\\
\noindent\textbf{Graph Generation}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
% Although the voxels vary between different datasets, the physical space remains constant. 
\\~\\
\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and ten negative examples. 
With probability 0.5, an example is reflected across the $xy$-plane. 
We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

### 2018-05-01 papers/quals2018/4_results.tex
quals: added method and evaluation from eccv submission
quals: major updates to structure

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
The results from our method are shown in red for varying the $\beta$ parameter. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

@@

\begin{table}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 974) compared to total number of edges in the graph (e.g., 25,798) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
\resizebox{\linewidth}{!}{
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 974 / 25,798 & 764 / 6,218 & 307 & 97 \\
		FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
		FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
	\end{tabular}
}
	\centering
	\label{table:skeletonization}
\end{table}

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
\\~\\
\noindent\textbf{Failure Cases}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases with the closest endpoints circled. 
In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 177 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning}
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{lee2017superhuman,zeng2017deepem3d}.
When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples show pairs of segments that belong to the same neuron but are not adjacent in the input segmentation. However, we correctly merge these pairs.}
	\label{fig:skeleton-results}
\end{figure}
Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.

\begin{figure}
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/receiver-operating-characteristic.png}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
	\label{fig:receiver-operating-characteristic}
\end{figure}

%\subsubsection{Generalization to Other Datasets}
%\noindent\textbf{Generalization to Other Datasets.}
Our neural network does not take as input the images or affinities so we can transfer network weights from one dataset to the next.
The classification results are comparable on the FlyEM datasets despite the fact that the data varies in resolution and even animal type from the training set.
\\~\\
%\subsection{Graph Optimization Results}
\noindent\textbf{Graph Partition}
The graph optimization strategy using multicut increases accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN with both the multicut and lifted multicut formulations.
These results correspond to $\beta = 0.95$ (Sec.~\ref{sec:edge-weights}). 
The precision increases on each dataset, although the recall decreases on each datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy increased the precision by $31.9\%$, $40.9\%$, and $27.8\%$ respectively.

\begin{table}[h]
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy. The lifted multicut extension provides very slight improvements in recall and accuracy over these three datasets.}
	\centering
\resizebox{\linewidth}{!}{
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri  & 31.94\% & -36.24\% & 0.71\% & -1.01\% & 0.60\% & 0.02\% \\
		FlyEM Vol. 1 & 40.87\% & -42.37\% & 1.26\% & 0.35\% & 0.85\% & 0.04\%  \\
		FlyEM Vol. 2 & 27.80\% & -44.95\% & 0.33\% & 0.54\% & 0.92\% & 0.04\% \\ \hline
	\end{tabular}
}
	\label{table:multicut}
\end{table}

\subsection{Computational Performance}
%\subsubsection{System} 
\noindent\textbf{System}
All performance experiments ran on an Intel Core i7-6800K CPU 3.40 GHz with a Titan X Pascal GPU. All code is written in Python and is freely available (link omitted for review). We use the Keras deep learning library for our neural networks with Theano backend and cuDNN 7 acceleration for CUDA 8.0.

Every step in our framework is fast enough for large connectomics datasets. 
On our training data, after downsampling, each segment was skeletonized in 0.56 seconds on average.
There are 4451 such segments resulting in a total running time of 2,492 seconds on an 800 megavoxel volume. 
From here, it took just over 31 seconds to generate the edges for our graph.
On our hardware, inference on the neural network has a throughput of 30 examples per second. 
Lastly, the multicut algorithm ran for 25.28 seconds while the lifted multicut variant took 36.5 seconds on the graph from this dataset.

>>>>

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

@@

\begin{table*}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 974) compared to total number of edges in the graph (e.g., 25,798) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
\resizebox{0.75\linewidth}{!}{
	\begin{tabular}{c c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Splits} & \textbf{Gained Edges} \\ \hline
		Kasthuri & 974 / 25,798 & 764 / 6,218 & 307 & 97 \\
		FlyEM Vol. 1 & 304 / 15,949 & 212 / 4,578 & 105 & 13 \\
		FlyEM Vol. 2 &  298 / 17,614 & 197 / 4,366 & 120 & 19 \\ \hline
	\end{tabular}
}
	\centering
	\label{table:skeletonization}
\end{table*}

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
\\~\\
\noindent\textbf{Failure Cases}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases with the closest endpoints circled. 
In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 177 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning}
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{lee2017superhuman,zeng2017deepem3d}.
When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.

\begin{figure}[t!]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate1.png}	
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}	
		\includegraphics[width=\linewidth]{./figures/merge_candidate2.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate3.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/merge_candidate4.png}
	\end{minipage}
	\caption{The top two examples correspond to segment pairs that we incorrectly prune from the graph. The distance between the circled endpoints is too great. The bottom two examples show pairs of segments that belong to the same neuron but are not adjacent in the input segmentation. However, we correctly merge these pairs.}
	\label{fig:skeleton-results}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/receiver-operating-characteristic.png}
	\caption{The receiver operating characteristic (ROC) curves of our classifier on three connectomics datasets. The classifier works best on previously unseen data of the Kasthuri volume.}
	\label{fig:receiver-operating-characteristic}
\end{figure}

%\subsection{Graph Optimization Results}
\noindent\textbf{Graph Partition}
The graph optimization strategy using multicut increases accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets compared to the CNN with both the multicut and lifted multicut formulations.
The precision increases on each dataset, although the recall decreases on each datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy increased the precision by $31.9\%$, $40.9\%$, and $27.8\%$ respectively.

\begin{table*}[h]
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy. The lifted multicut extension provides very slight improvements in recall and accuracy over these three datasets.}
	\centering
\resizebox{0.75\linewidth}{!}{
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri  & 31.94\% & -36.24\% & 0.71\% & -1.01\% & 0.60\% & 0.02\% \\
		FlyEM Vol. 1 & 40.87\% & -42.37\% & 1.26\% & 0.35\% & 0.85\% & 0.04\%  \\
		FlyEM Vol. 2 & 27.80\% & -44.95\% & 0.33\% & 0.54\% & 0.92\% & 0.04\% \\ \hline
	\end{tabular}
}
	\label{table:multicut}
\end{table*}

### 2018-05-01 papers/quals2018/6_compression.tex
quals: major updates to structure

\section{Compression}

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
		\hspace{0.08\linewidth}
		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
	\end{center}	
	\caption{Compresso works by dividing up the segmentation data into small blocks. On the left we show the intersection of three segments in a $4\times4\times1$ window. We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$. The location $i$ requires some additional bookkeeping. On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
	\label{fig:compression}
\end{figure*}

@@

General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.

@@

Our compression scheme outperforms all existing methods.
We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim670\times$.

>>>>

% !TEX root =  paper.tex
\section{Compression of Label Volumes}

@@

@@

Our compression scheme outperforms all existing methods.
We follow our scheme with LZMA which uses sophisticated probabilistic bit prediction strategies and achieve ratios of $700\times$ on average.
We compressed an 18 terabyte label volume of 100 microns cubed to 26.2 gigabytes, a ratio of $\sim687\times$.
